---
title: "Homework_1"
format: pdf
editor: visual
execute:
  echo: false
---

## Homework 1

The *ChickWeight* dataset is included in base R and documents the weight of chicks measured over time under different diets. It is often used for longitudinal data examples.

```{r}
# Load dataset
library(tidyverse)
data(ChickWeight)
head(ChickWeight)
```

Let's look at the number of observations and basic statistics of chick weights.

```{r}
summary(ChickWeight$weight)
table(ChickWeight$Diet)
length(unique(ChickWeight$Chick))
```

-   The data set contains multiple measurements of weight (weight) taken at different Time points.
-   There are 4 different diets applied to chicks.
-   There are multiple chicks (unique IDs) in the data set.

```{r}
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  labs(title = "Chick Weight Over Time by Diet",
       x = "Time (days)",
       y = "Weight (grams)",
       color = "Diet")
```

The scatter plot with smoothed lines reveals that chicks on Diet 3 and Diet 4 tend to gain weight more rapidly than those on Diets 1 and 2. This suggests potential differences in the effectiveness of the diets on chick growth over time.
